\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
This project implements solvers for three financial optimisation problems\+: {\bfseries Yield Curve Fitting}, {\bfseries Internal Rate of Return Estimation} and {\bfseries Bond Pricing} problems.

Some general guidelines and remarks are mentioned below.\hypertarget{index_template_guide}{}\section{Template Parameters}\label{index_template_guide}
A template parameter named {\bfseries T} denotes a floating-\/point number type.

A template parameter named {\bfseries F} denotes a lambda function (or function object/functor) type of the objective function

A template parameter named {\bfseries C} denotes a lambda function (or function object/functor) type of the constraints function

A template parameter named {\bfseries S} denotes a solver structure.\hypertarget{index_compile_guide}{}\section{Compilation}\label{index_compile_guide}
Compilation is possible with the three major compilers, gcc, clang and msvc.

Since some of the features used in the project are from the C++11/\+C++14 standards, the source has to be compiled with at least {\bfseries -\/std=c++14}.

For gcc and clang, {\bfseries -\/std=c++17} can be used as well, as the source is compatible with the newest C++ I\+SO standard.\hypertarget{index_external_libraries}{}\subsection{External Libraries}\label{index_external_libraries}
The external libraries used by the project are\+: {\bfseries Boost} (\href{http://www.boost.org/}{\tt http\+://www.\+boost.\+org/}) and {\bfseries date} (\href{https://github.com/HowardHinnant/date}{\tt https\+://github.\+com/\+Howard\+Hinnant/date}).

Boost is used for the Beta Distribution implementation and the pi constant.

date is used for date handling of the settlement and maturity dates.

Both can be included only as their header versions.\hypertarget{index_test_guide}{}\section{Showcase}\label{index_test_guide}
A showcase of the project is provided under {\bfseries \hyperlink{main_8cpp}{tests/main.\+cpp}}.

Be sure that the resulting executable will be run in the same working directory as the data files, otherwise the executable will crash abruptly, since exceptions are not implemented yet.

If other data files are used, be sure that their content has the correct format.

For bond data files, the input data have to be of the form\+: {\bfseries coupon rate (in percentage) price nominal value frequency settlement date (in yyyy-\/mm-\/dd form) and maturity date (in yyyy-\/mm-\/dd form)}.

For example\+: {\bfseries 0.\+06 101.\+657 100 2 2016-\/03-\/30 2019-\/06-\/24} has the correct format.

For interest rate data files, the input data have to be of the form\+: {\bfseries period (as a decimal) zero rate (in percentage)}.

For example\+: {\bfseries 0.\+25 0.\+079573813} has the correct format. 